Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-05-31 manuscript.Rmd
Add implications section

>>>>

## Implications

### Implications for Methodology

Nonlinear methods have been transformative for a variety of research
areas [including psychology, @coco2014cross]. One of the goals in the
present work was to introduce variants of one kind of nonlinear
method---specifically, recurrence quantification analysis---to
this research area. While a number of excellent guides can provide
detailed explanations of the methods and their statistical underpinnings 
[e.g., @riley2005tutorials; @webber1994dynamical; @webber2005recurrence],
one of the most important considerations that should be briefly
summarized here is about data.

Nonlinear methods---including recurrence-based analyses---require
time series data. This requires repeated observations of the behavior
at interest, preferably at a frequency that provides information 
about timing at a temporal resolution that allows the researcher to 
make observations about interesting variations over time. While
this is easily controlled by scientists who conduct experimental
research, it can be more difficult for scientists who rely on
trace data or naturally occurring data. However, where possible,
we recommend political scientists work to expand efforts for
improving the temporal granularity of the data. One possible
means of achieving this may be through collaborative efforts
like the Open Event Data Alliance [@schrodt2014three].

### Implications for Theory

(This would be where Leah should update her part.)
